### 2018-07-03 paper/1-intro.tex
Address suggestions of reviewers

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel, each in a dozen lines of code
or so (\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly.

>>>>

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel\footnote{\Excel appears very
different to the others but, seen through the lens of this paper, it is very
close indeed.}, each in a dozen lines of code or so
(\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly.
